Global study of well-being and internet adoption | Online analysis supplement

### 2021-11-22 01-clean.Rmd
Fix imputation
Space

# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions).We convert those to normal approximate standard errors.
gbd <- gbd %>% 
  mutate(se = (upper-lower) / (1.96*2)) %>%
  select(-c(upper, lower))
```

@@

```{r}
itu <- itu_long %>% 
  mutate(value = value_i) %>% 
  select(-value_i) %>% 
  pivot_wider()
rm(itu_long)
```

>>>>

# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions). We convert those to normal approximate standard errors.
gbd <- gbd %>% 
  mutate(se = (upper-lower) / (1.96*2)) %>%
  select(-c(upper, lower))
```

@@

```{r}
itu <- itu_long %>% 
  # Pick non-missing value, from original and imputed
  mutate(value = coalesce(value, value_i)) %>% 
  select(-value_i) %>% 
  pivot_wider()
rm(itu_long)
```
